%!TEX root =  ./proposal.tex

\section{Members of the consortium}

\eucommentary{This section is not covered by the page limit.}
\noindent
\eucommentary{The information provided here will be used to judge the operational capacity.}

\eucommentary{\begin{compactitem}
\item
Describe the consortium. How will it match the project's objectives?
How do the members complement one another (and cover the value chain,
where appropriate)? In what way does each of them contribute to the
project? How will they be able to work effectively together?
\item
If applicable, describe the industrial/commercial involvement in the
project to ensure exploitation of the results and explain why this is
consistent with and will help to achieve the specific measures which
are proposed for exploitation of the results of the project (see section 2.3).
\item
Other countries: If one or more of the participants requesting EU funding
is based in a country that is not automatically eligible for such funding
(entities from Member States of the EU, from Associated Countries and
from one of the countries in the exhaustive list included in General
Annex A of the work programme are automatically eligible for EU funding),
 explain why the participation of the entity in question is essential to carrying out the project
\end{compactitem}}

\subsection{Participants (applicants)}

\eucommentary{Please provide, for each participant, the following (if available):
\begin{compactitem}
\item a description of the legal entity and its main tasks, with an explanation of how its profile matches the tasks in the proposal;\item a curriculum vitae or description of the profile of the persons, including their gender, who will be primarily responsible for carrying out the proposed research and/or innovation activities;\item a list of up to 5 relevant publications, and/or products, services (including widely- used datasets or software), or other achievements relevant to the call content;\item a list of up to 5 relevant previous projects or activities, connected to the subject of this proposal;
\item a description of any significant infrastructure and/or any major items of technical equipment, relevant to the proposed work;
\item any other supporting documents specified in the work programme for this call.
\end{compactitem}}

\input{Participants/PAR1.tex}
\clearpage
\input{Participants/PAR2.tex}
\clearpage
\input{Participants/PAR3.tex}
\clearpage


%%% Local Variables:
%%% mode: latex
%%% TeX-master: "proposal"
%%% End:

