\providecommand{\classoptions}{keys}
\documentclass[noworkareas,deliverables,\classoptions]{euproposal}       % for writing
%\documentclass[submit,noworkareas,deliverables]{euproposal}        % for submission
%\documentclass[submit,public,noworkareas,deliverables]{euproposal} % for public version

\usepackage[utf8]{inputenc}

\usepackage{float}  % used to suppress floating of tables in Resources section.
\usetikzlibrary{calc,fit,positioning,shapes,arrows,snakes}
\usepackage[normalem]{ulem}

\addbibresource{kwarc.bib}
\input{WApersons} % Some sections of the included files depend on this.
\usepackage{comments}
\usepackage{framed}

% This is to reflect the EU template numbering scheme
\renewcommand*\thesection{\arabic{section}}

\begin{document}

\phantom{ }

\begin{proposal}[
  % These PM numbers (person months) are for the coordinator to help planning
  % Participants should not change these, but add PM numbers in the CVS in
  % the site descriptions at CVs/*.tex
  site=PAR1,
  site=PAR2,
  site=PAR3,
  site=PAR4,
  botupPM, % we want to work via bottom up PM distribution,
  coordinator=PAR1P1,
  coordinatorsite=PAR1,
  acronym={My-Prj-Acr},
  acrolong={My-Project-Acronym},
  title=My H2020 research project,
  callname=Call: Information and communication technologies,
  callid=Call identifier: H2020-ICT-2016-2017,
  keywords={science, research, ideas},
  instrument=Topic: Advanced robot capabilities research and take-up,
  challengeid =Challenge identifier: ICT-25-2016-2017,
  months=48,
  compactht]
\newcommand{\TheProject}{\pn}% \pn is defined automatically

\begin{center}
Proposal template (technical annex)
\end{center}
\begin{center}
Research and Innovation actions Innovation actions
\end{center}

Please follow the structure of this template when preparing your proposal. It has been designed to ensure that the important aspects of your planned work are presented in a way that will enable the experts to make an effective assessment against the evaluation criteria. Sections 1, 2 and 3 each correspond to an evaluation criterion for a full proposal.

Please be aware that proposals will be evaluated as they were submitted, rather than on their potential if certain changes were to be made. This means that only proposals that successfully address all the required aspects will have a chance of being funded. There will be no possibility for significant changes to content, budget and consortium composition during grant preparation.

\textbf{First stage proposals:} In two-stage submission schemes, at the first stage you only need to complete the parts indicated by a bracket (i.e. \}). These are in the cover page, and sections 1 and 2.

\textbf{Page limit:} \uline{For full proposals, the cover page, and sections 1, 2 and 3, together should not be longer than 70 pages}. All tables in these sections must be included within this limit. The minimum font size allowed is 11 points. The page size is A4, and all margins (top, bottom, left, right) should be at least 15 mm (not including any footers or headers).

\uline{The page limit for a first stage proposal is 10 pages.}
The page limit will be applied automatically; therefore you must remove this instruction page before submitting.

If you attempt to upload a proposal longer than the specified limit, before the deadline you will receive an automatic warning, and will be advised to shorten and re-upload the proposal. After the deadline, any excess pages will be overprinted with a 'watermark', indicating to evaluators that these pages must be disregarded.

Please do not consider the page limit as a target! It is in your interest to keep your text as concise as possible, since experts rarely view unnecessarily long proposals in a positive light.

\clearpage

\begin{abstract}
This was not in the EU community template ...
\end{abstract}


\ifsubmit\else\setcounter{tocdepth}{4}\fi
\tableofcontents
\clearpage

\TOWRITE{PAR1P1}{Larger table of participants}
\TOWRITE{PAR1P1}{Abstract in the first page?}
\TOWRITE{PAR1P1}{Centering}

\begin{draft}
\section*{Things to do \dots}
\TOWRITE{All}{Request from PAR1P1}
\subsection*{Things PAR1P1 asks as the consortium to do}
\begin{verbatim}
- [ ] Do things.
\end{verbatim}
\end{draft}


% ---------------------------------------------------------------------------
%  Section 1: Excellence
% ---------------------------------------------------------------------------

\section{Excellence}
\input{excellence.tex}

% ---------------------------------------------------------------------------
%  Section 2: Impact
% ---------------------------------------------------------------------------

\section{Impact}
\input{impact.tex}

% ---------------------------------------------------------------------------
%  Section 3: Implementation
% ---------------------------------------------------------------------------

\section{Implementation}

\input{implementation}

\input{WorkPackages/WorkPackages}

\clearpage
\gantttaskchart[draft,xscale=.23,yscale=.33,milestones]

\newpage
\subsubsection{Deliverables}\label{sec:deliverables}
\inputdelivs{9.3cm}

\newpage
\subsubsection{Milestones}\label{sec:milestones}
\input{milestones}

% ---------------------------------------------------------------------------
% Include Work package descriptions
% ---------------------------------------------------------------------------

\newpage
\subsection{Management Structure and Procedures}
\input{management_structure_and_procedures.tex}

\draftpage
\subsection{Consortium as a Whole}
\input{consortium.tex}
\draftpage

\subsection{Resources to be Committed}
\input{resources}

% ---------------------------------------------------------------------------
%  Section 4: Members of the Consortium
% ---------------------------------------------------------------------------

\newpage

\eucommentary{This section is not covered by the page limit.\\
The information provided here will be used to judge the operational capacity.}

\section{Members of the Consortium}

\subsection{Participants}

\eucommentary{Please provide, for each participant, the following (if available):\\
\begin{compactitem}
\item
a description of the legal entity and its main tasks,
with an explanation of how its profile matches the tasks in the proposal;
\item
a curriculum vitae or description of the profile of the persons,
including their gender, who will be primarily responsible for carrying
out the proposed research and/or innovation activities;
%
this includes a description of the profile of the to-be-recruited personnel
\item
a list of up to 5 relevant publications, and/or products, services
(including widely-used datasets or software), or other achievements
relevant to the call content;
\item
a list of up to 5 relevant previous projects or activities, connected
to the subject of this proposal;
\item
a description of any significant infrastructure and/or any major items
of technical equipment, relevant to the proposed work;
\item
any other supporting documents specified in the work programme for this call.
\end{compactitem}}

\input{Participants/PAR1.tex}
\clearpage
\input{Participants/PAR2.tex}
\clearpage
\input{Participants/PAR3.tex}
\clearpage

\subsection{Third Parties Involved in the Project (including use of third party resources)}
\label{section:ThirdParties}

\paragraph{Third Party 1}\ 

\eucommentary{Please complete, for each participant, the table
(see page 27 of "VRETemplate.PDF"),
or simply state "No third parties involved", if applicable.}

Third Party 1 (hereafter TP1) will work on the project.

\paragraph{Other participants}\ 

For other participants, the only subcontracting costs will be for audit.

\bgroup
\def\arraystretch{1.5}  % 1 is the default
\noindent \begin{tabular}{|p{0.6\textwidth}|c|}
\hline
Does the participant plan to subcontract certain
tasks & Yes \\
\hline
\multicolumn{2}{|l|}{Audit} \\
\hline
Does the participant envisage that part of its work
is performed by linked third parties & No \\
\hline
\multicolumn{2}{|l|}{} \\
\hline
Does the participant envisage the use of
contributions in kind provided by
third parties & No \\
\hline
\multicolumn{2}{|l|}{} \\
\hline
\end{tabular}
\egroup

%No third parties involved.

% ---------------------------------------------------------------------------
%  Section 5: Ethics and Security
% ---------------------------------------------------------------------------

\newpage

\section{Ethics and Security}

\eucommentary{This section is not covered by the page limit.}

\subsection{Ethics}

\eucommentary{
If you have entered any ethics issues in the ethical issue table in the administrative proposal forms, you must:\\
$\bullet$ submit an ethics self-assessment, which: \\
-- describes how the proposal meets the national legal and ethical requirements of the
country or countries where the tasks raising ethical issues are to be carried out;\\
-- explains in detail how you intend to address the issues in the ethical issues table, in
particular as regards:
research objectives (e.g. study of vulnerable populations, dual use, etc.),
research methodology (e.g. clinical trials, involvement of children and related
consent procedures, protection of any data collected, etc.),
the potential impact of the research (e.g. dual use issues, environmental damage,
stigmatisation of particular social groups, political or financial retaliation,
benefit-sharing, malevolent use , etc.)\\
$\bullet$ provide the documents that you need under national law (if you already have them), e.g.:\\
-- an ethics committee opinion;\\
-- the document notifying activities raising ethical issues or authorizing such activities\\
If these documents are not in English, you must also submit an English summary of them
(containing, if available, the conclusions of the committee or authority concerned).\\
If you plan to request these documents specifically for the project
you are proposing, your request must contain an explicit reference to the project title}

\subsection{Security}

Please indicate if your proposal will involve:

\begin{compactitem}
\item activities or results raising security issues: NO
\item 'EU-classified information' as background or results: NO
\end{compactitem}
\end{proposal}
\TOWRITE{ALL}{Search through final.pdf ('make final') and look for questions marks ?? and XX and YY and XYZ as place holders where people intended to later add a link, or where a link is broken.}
\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

